Sequential rank agreement methods for comparison of ranked lists

### 2015-06-22 latex/paper.Rnw
...

To interpretate the sequential rank agreement scale we propose by
several different benchmark values. Our data free benchmark value is
obtained by computing the sequential rank agreement of $L$ lists each
containing a permutation of $P$ items. Practically this benchmark
value can be obtained by averaging the result of repeated computer
experiments. In the uncensored case each experiment contains $L$ lists
of random permutations of the numbers $1,\dots,P$. In the censored
case only the uncensored part of the orginal lists is randomly
permuted.

>>>>

To interpret the sequential rank agreement values we propose two
different benchmark values corresponding to two different
hypotheses. We wish to determine if we observe better agreement that
what would be expected if there were no relevant information available
in the data.

The first reference hypothesis is 
\begin{eqnarray*}
H_0  & : &  \text{The list rankings correspond to complete randomly}\\
       &  & \text{permuted lists} \\
\end{eqnarray*}

\begin{eqnarray*}
H_1 & :&  \text{The list rankings correspond to ranked lists based on}\\
& &   \text{data containing no information}
\end{eqnarray*}

It is important to stress 
Note that

Compute the sequential rank agreement for a large number of random
permutations ... with the same number of lists and with the same amount of censoring.

understood about the outcome

Clearly hypothesis .... is ... no association and that the methods are
also completely independent.

Our data free benchmark value is
obtained by computing the sequential rank agreement of $L$ lists each
containing a permutation of $P$ items. Practically this benchmark
value can be obtained by averaging the result of repeated computer
experiments. In the uncensored case each experiment contains $L$ lists
of random permutations of the numbers $1,\dots,P$. In the censored
case only the uncensored part of the orginal lists is randomly
permuted.
